### 2019-11-28 ch10_discussion/content.tex
small update discussion

@@

Software bugs can be introduced even by incredibly small, seemingly insignificant changes. The R programming language seems particularly susceptible towards getting trapped by its many pitfalls. However, there are many benefits of using R in bioinformatics research context, such as its extensive community of statisticians develop packages for the R ecosystem. The \textbf{tidyverse} packages \cite{wickham_tidytoolsmanifesto_2017}, developed by the RStudio team and many online contributors, completely transformed my experiences with R from tedious struggles to efficient everyday functional programming.

>>>>

\section{Trajectory inference}

\section{Network inference}

\section{Benchmarking in bioinformatics}

@@

Software bugs can be introduced even by incredibly small, seemingly insignificant changes. The R programming language seems particularly susceptible towards getting trapped by its many pitfalls. However, there are many benefits of using R in bioinformatics research context, such as its extensive community of statisticians develop packages for the R ecosystem. The \textbf{tidyverse} packages \cite{wickham_welcometidyverse_2019}, developed by the RStudio team and many online contributors, completely transformed my experiences with R from tedious struggles to efficient everyday functional programming.
